The Role of Video Data Sharing in Advancing Education Policy and Practice

### 2015-05-09 2015-06-01-nsf-ed-workshop/paper.tex
add Nosek2012, edit future of technology and conclusion

Unfortunately, despite the efforts of professional organizations to make data sharing a norm \cite{AERA-Code-2011} most research on human development and learning remains shrouded in a culture of isolation. 
Rather than providing direct access to raw data, researchers in the developmental and learning sciences share interpretations of distilled data almost exclusively through publications and presentations.
The path from raw data to finding to conclusion cannot be traced or validated by others, nor can new questions be posed by others building on the same, often expensive-to-collect, raw data.
To realize significant advances in our understanding of teaching and learning and for those insights to have meaningful impact on educational practice and policy, open data sharing must become an established norm, not the rare exception.
Moreover, we must find ways to share the most valuable raw data, the data with the greatest potential for reuse by others, and the data with the greatest potential for yielding meaningful insights into the learning process.

@@

The Databrary team recognizes that other data repositories enforce strict metadata ontologies and that these Doing may have benefits in sub-domains of research when there is community consensus on core concepts. 
The Databrary team has chosen not to require strict metadata ontologies for several reasons. 
We hope to reduce the pre-deposit curational demands on contributors and foster the rapid adoption of data sharing.Developing and achieving agreement on metadata ontologies can take significant amounts of time. 
Video data are so rich and complex that in many domains, researchers have not settled on standard definitions for particular behaviors and may have little current need for standard tasks, procedures, or terminology. 
However, Databrary empowers users to re-use tags and terminology by suggesting common or similar terms, without confining users to these suggestions. 
User communities within Databrary may eventually converge on common conceptual and metadata ontologies based on the most common (and commonly endorsed) keyword tags, but standardized ontologies are not necessary for browsing and searching in most of the use cases we envision.
Future challenges include building the capacity to searching for tagged segments inside of videos.
Some of within-video tagging functionality exists in the current software, with more extensive search and preview capabilities on the near horizon.

The Databrary team believes that the effort spent creating this powerful and flexible system will enable it to be extended to a diverse communities engaged in educational research.

@@

Equally important for the success of a video data sharing enterprise are policies for openly identifiable data in ways that securely preserve participant privacy.
As discussed previously, videos cannot be easily or cheaply de-identified without undermining their reuse value.
Databrary has chosen to maximize the potential for data re-use by keeping recordings in their original
unaltered form.
To make unaltered raw videos available to others for reuse, Databrary has developed a two-pronged access model that i) restricts access to authorized individuals, and ii) enables access to identifiable data only with the permission of the people depicted.

@@

Video has considerable untapped potential for making tangible the anatomy of successful teaching and learning.
Realizing this potential requires a multifaceted approach that reduces barriers to sharing video and fosters new community values that embrace it.
The Databrary project has built technology and policies that overcome many of the most significant barriers to widespread video data sharing within the developmental sciences community, including solutions to maintaining participant privacy, data tagging, and data management., 
Databrary suggests ways that video and other identifiable data collected in the context of education research might also be shared.
Widespread open sharing of high value, high impact data promises to advance education policy and improve practice.
The Databrary team welcomes collaborations with other like-minded parties who share our vision \cite{Adolph2012} for a future where open data sharing is the norm in the behavioral and social sciences.

>>>>

Unfortunately, despite the efforts of professional organizations to make data sharing a norm \cite{AERA-Code-2011} most research on human development and learning \cite{Adolph2012} and in the social sciences in general \cite{Nosek2012} remains shrouded in a culture of isolation. 
Rather than providing direct access to raw data, researchers in the developmental and learning sciences share interpretations of distilled data almost exclusively through publications and presentations.
The path from raw data to finding to conclusion cannot be traced or validated by others, nor can new questions be posed by others building on the same, often expensive-to-collect, raw data.
To realize significant advances in our understanding of teaching and learning and for those insights to have meaningful impact on educational practice and policy, open data sharing must become an established norm, not the rare exception.
Moreover, we must find ways to share the most valuable raw data, the data with the greatest potential for reuse by others, and the data with the greatest potential for yielding meaningful insights into the learning process.

@@

The Databrary team recognizes that other data repositories enforce strict metadata ontologies and that these Doing may have benefits in sub-domains of research when there is community consensus on core concepts. 
The Databrary team has chosen not to require strict metadata ontologies for several reasons. 
We hope to reduce the pre-deposit curational demands on contributors and foster the rapid adoption of data sharing.Developing and achieving agreement on metadata ontologies can take significant amounts of time. 
Video data are so rich and complex that in many domains, researchers have not settled on standard definitions for particular behaviors and may have little current need for standard tasks, procedures, or terminology. 
However, Databrary empowers users to re-use tags and terminology by suggesting common or similar terms, without confining users to these suggestions. 
User communities within Databrary may eventually converge on common conceptual and metadata ontologies based on the most common (and commonly endorsed) keyword tags, but standardized ontologies are not necessary for browsing and searching in most of the use cases we envision.

Future challenges include building the capacity to searching for tagged segments inside of videos.
Some of within-video tagging functionality exists in the current software, with more extensive search and preview capabilities on the near horizon.
A related challenge involves developing mechanisms that enable files from video coding tools to be imported into Databrary so that user supplied codes may be visualized independent of the desktop coding tool deployed in a particular project.
We envision a parallel set of export functions that permit full interoperability among coding tools.
Since some tools use proprietary data formats, the priority will be to create interoperability with tools using open formats.
The Databrary team believes that the effort spent creating this powerful and flexible system will enable it to be extended to a diverse set of communities engaged in educational research who collect and seek to share video.

@@

Equally important for the success of a video data sharing enterprise are policies for openly identifiable data in ways that securely preserve participant privacy.
As discussed previously, videos cannot be easily or inexpensively deidentified without undermining their reuse value.
Databrary has chosen to maximize the potential for data reuse by keeping recordings in their original
unaltered form.
To make unaltered raw videos available to others for reuse, Databrary has developed a two-pronged access model that i) restricts access to authorized individuals, and ii) enables access to identifiable data only with the permission of the people depicted.

@@

Video has considerable untapped potential for making tangible the anatomy of successful teaching and learning.
Realizing this potential requires a multifaceted approach that reduces barriers to sharing video and fosters new community values that embrace it.
The Databrary project has built technology and policies that overcome many of the most significant barriers to widespread video data sharing within the developmental sciences community, including solutions to maintaining participant privacy, data tagging, and data management. 
Databrary suggests ways that video and other identifiable data collected in the context of education research might also be shared.
Technologies and policies for providing secure access to videos for broader use cases will have to be developed, and tools that allow desktop coding software files to be seamlessly imported to and exported from Databrary will have to be perfected.
Communities of scholars dedicated to sharing education-related video will have to be cultivated.
But, we believe that the widespread sharing of high value, high impact data of the sort that video can provide promises to advance education policy and improve practice.
The Databrary team welcomes collaborations with other like-minded parties who share our vision \cite{Adolph2012} for a future where open data sharing is the norm.
